### 2015-07-15 thesis/thesis/abstract.tex
change

In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise. The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities. There are a number of proposed mechanisms and models on aggregating web services and making them cooperate within their communities. However, forming optimal and stable communities as coalitions to maximize individual and group efficiency and income for all the involved parties has not been addressed yet. Moreover, in the proposed frameworks of these communities, a common assumption is that residing services, which are supposed to be autonomous and intelligent, are competing over received requests. However, those services can also exhibit cooperative behaviors, for instance in terms of substituting each other. When competitive and cooperative behaviors and strategies are combined, autonomous services are said to be ``coopetitive''. Deciding to compete or cooperate inside communities is a problem yet to be investigated.

In this thesis, we first identify the problem of defining efficient algorithms for coalition formation mechanisms. We study the community formation problem in two different settings: 1) Communities with centralized manager having complete information using cooperative game-theoretic techniques. 2) Communities with distributed decision making mechanisms having incomplete information using training methods. We propose mechanisms for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities. Then in order to address the coopetitive relation within communities of web services, we propose a decision making mechanism for our web services to efficiently choose competition or cooperation strategies to maximize their payoffs. We prove that the proposed decision mechanism is efficient and can be implemented in time linear in the length of the time period considered for the analysis and the number of services in the community. Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real web services dataset.

>>>>

In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise. The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities. There are some proposed mechanisms and models on aggregating web services and making them cooperate within their communities. However, forming optimal and stable communities as coalitions to maximize individual and group efficiency and income for all the involved parties has not been addressed yet. Moreover, in the proposed frameworks of these communities, a common assumption is that residing services, which are supposed to be autonomous and intelligent, are competing over received requests. However, those services can also exhibit cooperative behaviors, for instance in terms of substituting each other. When competitive and cooperative behaviors and strategies are combined, autonomous services are said to be ``coopetitive''. Deciding to compete or cooperate inside communities is a problem yet to be investigated.

In this thesis, we first identify the problem of defining efficient algorithms for coalition formation mechanisms. We study the community formation problem in two different settings: 1) communities with centralized manager having complete information using cooperative game-theoretic techniques; and 2) communities with distributed decision making mechanisms having incomplete information using training methods. We propose mechanisms for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities. Then in order to address the coopetitive relation within communities of web services, we propose a decision making mechanism for our web services to efficiently choose competition or cooperation strategies to maximize their payoffs. We prove that the proposed decision mechanism is efficient and can be implemented in time linear in the length of the time period considered for the analysis and the number of services in the community. Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real web services dataset.

### 2015-07-15 thesis/thesis/chap1/chap1.tex
change

In order to address the centralized decision making process limitations and adopt a distributed decision making approach, we introduce DDM\footnote{This contribution is submitted to International Journal of Decision Support Systems as a journal paper}, a Distributed Decision Making model for community formation. DDM regulates web service agents' decision making process in terms of cooperating and deciding which group to join and which service to invite for joining. Unlike existing work on community formation, our decision model is extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The generated decision tree improves agents' understanding of the environment and and helps them select actions that lead towards maximizing their utilities. The advantage of this approach is that the tree, which is initially created from the past data, reflects a comprehensive vision about agents' attitudes in terms of their action selection based on their past experiences. Moreover, the tree is getting continuously updated based on both new received feedback and the outcome of chosen actions. This continuous update makes the approach adaptable to any change in the environment.
%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems.
The decision model provides web services with enough information which helps those services efficiently decide and predict the outcome of their different possible collaborations. This model works in a distributed manner in which services are self-sufficient in their decision making and do not rely on a centralized decision making process. Our findings show that communities of web services can efficiently find the appropriate web service to invite for cooperation as well as allowing a single web service to find the best communities to join. The proposed model can be seen as a recommneder system that suggests beneficial actions for both communities and single services. Communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact both their short-term and long-term goals; therefore, opting for the best decision available.

@@

In previous contributions, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents. In our next contribution\footnote{This contribution was published in \cite{DBLP:journals/eswa/AslBMKO14}} our focus is on the internal management affairs of communities of web services. Within communities, the web services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}. When competitive and cooperative behaviors and strategies are combined, autonomous services are said to be ``coopetitive''. In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite. However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure. Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section. we propose a mechanism within which service agents
in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this thesis interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task. We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate). In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility. We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.

>>>>

In order to address the centralized decision making process limitations and adopt a distributed decision making approach, we introduce DDM\footnote{This contribution is submitted to International Journal of Decision Support Systems}, a Distributed Decision Making model for community formation. DDM regulates web service agents' decision making process in terms of cooperating and deciding which group to join and which service to invite for joining. Unlike existing work on community formation, our decision model is extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The generated decision tree improves agents' understanding of the environment and and helps them select actions that lead towards maximizing their utilities. The advantage of this approach is that the tree, which is initially created from the past data, reflects a comprehensive vision about agents' attitudes in terms of their action selection based on their past experiences. Moreover, the tree is getting continuously updated based on both new received feedback and the outcome of chosen actions. This continuous update makes the approach adaptable to any change in the environment.
%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems.
The decision model provides web services with enough information which helps those services efficiently decide and predict the outcome of their different possible collaborations. This model works in a distributed manner in which services are self-sufficient in their decision making and do not rely on a centralized decision making process. Our findings show that communities of web services can efficiently find the appropriate web service to invite for cooperation as well as allowing a single web service to find the best communities to join. The proposed model can be seen as a recommneder system that suggests beneficial actions for both communities and single services. Communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact both their short-term and long-term goals; therefore, opting for the best decision available.

@@

In the previous contributions, our focus was on community formation and we emphasized cooperative behavior of the web services as agents. In our next contribution\footnote{This contribution was published in \cite{DBLP:journals/eswa/AslBMKO14}} our focus is on the internal management affairs of communities of web services. Within communities, the web services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}. When competitive and cooperative behaviors and strategies are combined, autonomous services are said to be ``coopetitive''. In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite. However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure. Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section. we propose a mechanism within which service agents
in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this thesis interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task. We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate). In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility. We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.

### 2015-07-15 thesis/thesis/chap2/chap2.tex
behaivour
change

        Core stability is a highly desirable property however in many problems it is not achievable. It would be more ideal to maintain a set of somewhat stable payoffs when the core is empty. There are several approaches to achieve this goal. One may drop the stability requirement and focus on other types of solutions for which a payoff division is guaranteed to exist. Two well known solution concepts in this category are \emph{nucleolus} \cite{schmeidler_nucleolus_1969} and the \emph{bargaining set} \cite{Davis67existenceof}. They try to minimize some measure of unhappiness in the game for the agents.

@@

        A community can also be stabilized by relaxing the core constraints. According to \emph{Core}, an outcome is unstable if a coalition can benefit even by a small amount from deviating, which is a strong requirement. In fact, in some situations, deviations can be costly, or players may have loyalty to their coalitions, or even it can be computationally intractable to find those small benefits. It would only make sense for a coalition to deviate if the gain from a deviation exceeds the cost of performing the deviation. \emph{$\epsilon$-core} relaxes the notion of the core, and only requires that no coalition would benefit significantly, or within a constant amount($\epsilon$) by deviating (see Equation \ref{eq:core3}).

@@

\subsection{Coopetitive Behaviour Within Communities of Web Services}\label{sec:coopetetive}

@@

In this thesis, as the first contribution, we will tackle the issue of community formation in an efficient way for all the web services and communities involved. We will use game theory to propose a cooperative game model for the aggregation of web services within communities. The solution concepts of our cooperative game seeks to find efficient ways of forming coalitions (teams) of web services so that they can maximize their gain and payoff, and distribute the gain in a fair way among all the web services. Achieving fairness when the gain is distributed among the community members is the main factor to keep the coalition stable as no web service will expect to gain better by deviating from the community. In other words, the coalition is made efficient if all the members are satisfied. We first propose a representation function for communities of web services based on their QoS attributes. By using this function, we can evaluate the $worth$ of each community of web services. When facing new membership requests, a typical community master checks whether the new coalition having the old and new set of web services will keep the community stable or not. The community master will reject the membership requests if it finds out that the new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more by deviating from the community and joining other communities or forming new ones. The computation of solutions for cooperative game theory problems is combinatorial in nature and proven to be NP-complete \cite{Algorithmic}, making this computation impractical in real world applications. However, using the concepts of coalition stability, we propose approximation algorithms running in polynomial time providing web services and community masters with applicable and near-optimal decision making mechanisms.

Next we will tackle the issue of distributed model of web services and propose a decision model for scenarios where information is incomplete. We proposed a training model for the problem of membership management of communities of web services. Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves. This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available. The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms. The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.

In our last contribution, the focus is on internal community management. We proposed a game-theoretic based model to analyze the best efficiency characteristics for the active services in open networks. The proposed framework considers the chances of web services in joining a community in different cases with truthful and lying information service agents. The proposed game analyzes the existing Nash equilibrium and situations where the maximum payoff is obtained.

>>>>

        Core stability is a highly desirable property. However, in many problems this property is not achievable. It would be more ideal to maintain a set of quasi-stable payoffs when the core is empty. There are several approaches to achieve this goal. One may drop the stability requirement and focus on other types of solutions for which a payoff division is guaranteed to exist. Two well known solution concepts in this category are \emph{nucleolus} \cite{schmeidler_nucleolus_1969} and the \emph{bargaining set} \cite{Davis67existenceof}. They try to minimize some measure of unhappiness in the game for the agents.

@@

        A community can also be stabilized by relaxing the core constraints. According to \emph{Core}, an outcome is unstable if a coalition can benefit even by a small amount from deviating, which is a strong requirement. In fact, in some situations, deviations can be costly, or players may have loyalty to their coalitions, or even it can be computationally intractable to find those small benefits. It would only make sense for a coalition to deviate if the gain from a deviation exceeds the cost of performing the deviation. \emph{$\epsilon$-core} relaxes the notion of the core, and only requires that no coalition would benefit significantly, or within a constant amount ($\epsilon$) by deviating (see Equation \ref{eq:core3}).

@@

\subsection{Coopetitive Behavior Within Communities of Web Services}\label{sec:coopetetive}

@@

In this thesis, as the first contribution, we will tackle the issue of community formation in an efficient way for all the web services and communities involved. We will use game theory to propose a cooperative game model for the aggregation of web services within communities. The solution concepts of our cooperative game seeks to find efficient ways of forming coalitions (teams) of web services so that they can maximize their gain and payoff, and distribute the gain in a fair way among all the web services. Achieving fairness when the gain is distributed among the community members is the main factor to keep the coalition stable as no web service will expect to gain better by deviating from the community. In other words, the coalition is made efficient if all the members are satisfied. We first propose a representation function for communities of web services based on their QoS attributes. By using this function, we can evaluate the $worth$ of each community of web services. When facing new membership requests, a typical community master checks whether the new coalition having the old and new set of web services will keep the community stable or not. The community master will reject the membership requests if it finds out that the new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more by deviating from the community and joining other communities or forming new ones. The computation of solutions for cooperative game theory problems is combinatorial in nature and proven to be NP-complete \cite{Algorithmic}, making this computation impractical in real world applications. However, using the concepts of coalition stability, we proposed approximation algorithms running in polynomial time providing web services and community masters with applicable and near-optimal decision making mechanisms.

Next, we will tackle the issue of distributed model of web services and propose a decision model for scenarios where information is incomplete. We will propose a training model for the problem of membership management of communities of web services. Using the traning model we aim to create a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves. This will equip our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available. The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices. 
%The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms. The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.

In our last contribution, the focus is on internal community management. We will introduce a game-theoretic based model to analyze the efficiency characteristics for the active services in open networks. The proposed framework will consider the chances of web services in joining a community in different cases with truthful and lying information service agents. The proposed game will analyze the existing Nash equilibrium and situations where the maximum payoff is obtained.

### 2015-07-15 thesis/thesis/chap3/chap3.tex
change

In this chapter, we present our coalition model of agent-based web
services within communities \cite{SCC2013efficient}. We start by describing the general
architecture and considered parameters for web services.
Thereafter, problem modeling and formulation will be introduced in
terms of task distribution and community revenue. Web service
cooperative games in different settings will follow along with
some simulation results.

@@

In this chapter, we assumed our web services and communities have compelte knowledge of all the other web services and their parameters. In next chapter we propose distributed decision making model which can perform in scenarios where information is incomplete.

>>>>

In this chapter, we present our coalition model of agent-based web
services within communities \cite{SCC2013efficient}. We start by describing the general
architecture and considered parameters for web services.
Thereafter, problem modeling and formulation will be introduced in
terms of task distribution and community revenue. Web service
cooperative games in different settings will follow along with simulation results.

@@

In this chapter, we assumed our web services and communities have complete knowledge of all the other web services and their parameters. In the next chapter, we propose distributed decision making model which can perform in scenarios where information is incomplete.

### 2015-07-15 thesis/thesis/chap4/chap4.tex
change

\subsubsection{Input Web Services Data}\label{sss:webservices}

@@

\subsubsection{Feature Extraction}\label{sss:filtereddata}

@@

\subsubsection{Feature Engineering}\label{sss:feng}
Let $CFVS = \{CFV_{<C_1>}, \dots, CFV_{<C_N>}\}$ be the community feature vector set with $N$ communities. Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix $gain^{t}$ for each time slot $t$. Each entry $gain_{n,m}^{t}$ corresponds to a utility gain of community $C_n$ when it joins community $C_m$. This gain is computed as follows: $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$ where $U_{C_n \cup C_m}^{t}$ and $U_{C_{n}}^{t}$ are the utilities at time $t$ computed using Equation \ref{u_c_load}.  Evaluating the utility gain for all entries of the $gain^t$ matrix is a computationally heavy process when $N$, the size  of the feature vector set, is large. Therefore, this size should be chosen carefully.

@@

In this research work, we proposed a training model for the problem of membership management of communities of web services. Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves. This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available. The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms. The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.

@@

In next chapter, we analyse the internal community behavior of web services, and propose a model for competing and cooperating agents within the communities of web services.

>>>>

\bigskip
\noindent \textbf{A. Input Web Services Data}\label{sss:webservices}

@@

\bigskip
\noindent \textbf {B. Feature Extraction}\label{sss:filtereddata}

@@

\bigskip
\noindent \textbf {C. Feature Engineering}\label{sss:feng}

Let $CFVS = \{CFV_{<C_1>}, \dots, CFV_{<C_N>}\}$ be the community feature vector set with $N$ communities. Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix $gain^{t}$ for each time slot $t$. Each entry $gain_{n,m}^{t}$ corresponds to a utility gain of community $C_n$ when it joins community $C_m$. This gain is computed as follows: $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$ where $U_{C_n \cup C_m}^{t}$ and $U_{C_{n}}^{t}$ are the utilities at time $t$ computed using Equation \ref{u_c_load}.  Evaluating the utility gain for all entries of the $gain^t$ matrix is a computationally heavy process when $N$, the size  of the feature vector set, is large. Therefore, this size should be chosen carefully.

@@

In this research work, we proposed a training model for the problem of membership management of communities of web services. Using the training model, we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves. This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, which allowed them to make better decisions. The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms. The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.

@@

In the next chapter, we analyse the internal community behavior of web services, and propose a model for competing and cooperating agents within the communities of web services.

### 2015-07-15 thesis/thesis/chap5/chap5.tex
change

In previous chapter, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents. Within communities, the web services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}. In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite. However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure. Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section. we propose a mechanism within which service agents
in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this report interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task. We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate). In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility. We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.

@@

In this section, we provide an empirical analysis over the
theoretical results regarding the characteristics of intelligent
service agents hosted in different communities of services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, service agents as service providers, and
master agents as community representatives.
%These entities are developed with respect to what is explained in Section \ref{s4:Preliminaries}.
In this section, the objective is to
investigate the effectiveness of the proposed strategic system on
intelligent services' overall budget and also the average quality
and quantity of tasks performed by the community of services,
which directly affects user satisfaction.
%Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
To verify these objectives, we study the overall performance of
the community hosting the reasoning-empowered services compared to
the ones hosting stochastic and purely competitive services. By
stochastic services, we mean services that adopt at each moment
competitive or cooperative strategies in an equally but random
way. By equally, we mean the choices are fairly divided between
the two strategies.

@@

In this chapter, we proposed a game-theoretic based model to analyze the best efficiency characteristics for the active services in open networks. The proposed framework considers the chances of web services in joining a community in different cases with truthful and lying information service agents. The proposed game analyzes the existing Nash equilibrium and situations where the maximum payoff is obtained.

Our model has the advantage of being simple and taking into account three important factors: (1) rational web services seek better status in the environment by joining the community; (2) rational web services obtain higher payoff by truth telling; and (3) the community is obtaining more effective web services
%As future work, we plan to consider the user role in the game to obtain more accurate results when users act rationally. Moreover, we would like to achieve a collusion resistant efficiency mechanism, which is still an open problem in open environments.

>>>>

In the previous chapter, our focus was on community formation and we emphasized cooperative behavior of the web services as agents. Within communities, the web services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}. In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite. However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure. Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section. we propose a mechanism within which service agents
in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this report interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task. We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate). In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility. We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.

@@

In this section, we provide an empirical analysis over the
theoretical results regarding the characteristics of intelligent
service agents hosted in different communities of services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, service agents as service providers, and
master agents as community representatives.
%These entities are developed with respect to what is explained in Section \ref{s4:Preliminaries}.
The objective is to investigate the effectiveness of the proposed strategic system on
intelligent services' overall budget and also the average quality
and quantity of tasks performed by the community of services,
which directly affects user satisfaction.
%Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
To verify these objectives, we study the overall performance of
the community hosting the reasoning-empowered services compared to
the ones hosting stochastic and purely competitive services. By
stochastic services, we mean services that adopt at each moment
competitive or cooperative strategies in an equally but random
way. By equally, we mean the choices are fairly divided between
the two strategies.

@@

In this chapter, we proposed a game-theoretic based model to analyze the efficiency characteristics for the active services in open networks. The proposed framework considers the chances of web services in joining a community in different cases with truthful and lying information service agents. The proposed game analyzes the existing Nash equilibrium and situations where the maximum payoff is obtained.

Our model has the advantage of being simple and taking into account three important factors: (1) rational web services seek better status in the environment by joining the community; (2) rational web services obtain higher payoff by truth telling; and (3) the community is obtaining more effective web services. These advantages are confirmed through the conducted simulations.
%As future work, we plan to consider the user role in the game to obtain more accurate results when users act rationally. Moreover, we would like to achieve a collusion resistant efficiency mechanism, which is still an open problem in open environments.

### 2015-07-15 thesis/thesis/chap6/chap6.tex
change

In this theses, we proposed three models for aggregation of web services within communities. The goal of our models are to maximize efficiency by collaborating and forming stable communities. In our first contributions, we focused on stability and fairness for all web services within the communities. In this work we addressed the shortcomings of community formation in recent work such as considering best strategies which benefit all services involved, making solutions practical in real-time settings and also fairness and stability of communities. The proposed model offers an applicable mechanism for membership requests and selection of web services. The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more tasks with high quality. The theoretical and extensive simulation results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-optimal decision making mechanisms.

In our next step of research work, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and membership management in communities of web services. In this work we tried to tackle the issue of autonomous web services not having a centralized architecture and complete information of all the parameters of other web services. The proposed mechanism helps web services and communities decide with whom to be grouped and cooperate. DDM first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Communities and web services can use the trained model and instantly choose best-response strategies considering their long-term gain. In fact, the decision making mechanism is implemented as a decision tree of possible viable strategies along with their long-term expected utility. The ultimate goal of our mechanism is to make a better decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature. We performed excrements using real date from 142 users on 4,532 web services during 64 different time slots. The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions. Moreover, the experiments using real data samples support the need for a long-term training model in a successful decision making process.

In our final step of the work, the focus was on inter-community interaction between services involved within the community. The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behavior of intelligent services that are active within communities. We considered two acting strategies where service agents expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers. Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes. The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities. The theoretical results presented in this thesis are also backed by simulation results using a real services dataset. Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real services dataset on the web. Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
services deviate from the coopetitive strategy suggested by our decision-making mechanism the less benefits they make.

@@

As future work, for the community formation in our first model, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal
$\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications. From web service perspective, the work can be extended to consider web services compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperative game theory concepts\cite{RePEc:roc:rocher:554} can be used to help web services resolve the instability and unfairness issues by side payments.

For the distributed model, our future plan is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches. Hedonic games and fractional hedonic games\cite{Brandl:2015:FHG:2772879.2773307, Aziz_GGMT_70} are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members. We intent to investigate stability solution concepts such as Shapely value so that long-term decisions will be based on the probability that the community will last for long period. The SVM machine learning algorithm\cite{Osuna97trainingsupport, Cortes:1995:SN:218919.218929} is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs. This can further facilitate the process of finding optimal cooperators in which will result in enhancing web services' overall performance as service providers.

@@

\item F. Al-Saqqar, J. Bentahar, K. Sultan, W. Wan, E. Khosrowshahi Asl, "Model checking temporal knowledge and commitments in multi-agent systems using reduction", Journal of Simulation Modelling Practice and Theory, 2015.

@@

>>>>

In this thesis, we proposed three models for aggregation of web services within communities. The goal of our models are to maximize efficiency by collaborating and forming stable communities. In our first contribution, we focused on stability and fairness for all web services within the communities. In this work, we addressed the shortcomings of community formation in recent work such as considering best strategies which benefit all services involved, making solutions practical in real-time settings and taking into account the fairness and stability of communities. The proposed model offers an applicable mechanism for membership requests and selection of web services. The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more tasks with high quality. The theoretical and extensive simulation results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-optimal decision making mechanisms.

In our next step of research work, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and membership management in communities of web services. In this work, we tried to tackle the issue of autonomous web services not having a centralized architecture and complete information of all the parameters of other web services. The proposed mechanism helps web services and communities decide with whom to be grouped and cooperate. DDM first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Communities and web services can use the trained model and instantly choose best-response strategies considering their long-term gain. In fact, the decision making mechanism is implemented as a decision tree of possible viable strategies along with their long-term expected utility. The ultimate goal of our mechanism is to make a better decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature. We performed experiments using real date from 142 users on 4,532 web services during 64 different time slots. The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions. Moreover, the experiments using real data samples support the need for a long-term training model in a successful decision making process.

In our final step of the work, the focus was on inter-community interaction between services involved within the community. The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behavior of intelligent services that are active within communities. We considered two acting strategies where service agents expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers. Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes. The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities. The theoretical results presented in this thesis are also backed by simulation results using a real services dataset. Moreover, we conducted extensive simulations, analyzed various scenarios, and confirmed the obtained theoretical results using parameters from a real services dataset on the web. Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
services deviate from the coopetitive strategy suggested by our decision-making mechanism the less benefits they make.

@@

As future work, for the community formation in our first model, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal
$\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications. From web service perspective, the work can be extended to consider web services compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperative game theory concepts \cite{RePEc:roc:rocher:554} can be used to help web services resolve the instability and unfairness issues by side payments.

For the distributed model, our future plan is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches. Hedonic games and fractional hedonic games \cite{Brandl:2015:FHG:2772879.2773307, Aziz_GGMT_70} are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members. We intent to investigate stability solution concepts such as Shapely value so that long-term decisions will be based on the probability that the community will last for long period. The SVM machine learning algorithm \cite{Osuna97trainingsupport, Cortes:1995:SN:218919.218929} is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs. This can further facilitate the process of finding optimal cooperators which will result in enhancing web services' overall performance as service providers.

@@

@@

\textbf{Collaborated works}

\begin{itemize}
\item F. Al-Saqqar, J. Bentahar, K. Sultan, W. Wan, E. Khosrowshahi Asl, "Model checking temporal knowledge and commitments in multi-agent systems using reduction", Journal of Simulation Modelling Practice and Theory, 2015.
\end{itemize}
